---
title: "Tutorial 5"
author: "Yong Kok Khuen (17147279)"
date: "11/22/2021"
output: html_document
---

Code: [GitHub](https://github.com/yongkokkhuen/pds-tutorial/blob/main/Tutorial-5.Rmd)

Load "attitude" data set

```{r}
library(datasets)
df <- attitude
```

1. See basic descriptive statistics

```{r}
summary(df)
```

1. a) Difference between **attitude[3]** and **attitude$learning**

```{r}
attitude[3]
```

```{r}
attitude$learning
```

```{r}
typeof(attitude[3])
```

```{r}
is.list(attitude[3])
```

```{r}
typeof(attitude$learning)
```

```{r}
is.vector(attitude$learning)
```

Answer: **attitude[3]** returns a list, **attitude$learning** returns a vector.

2. Lists name of variables in a data set

```{r}
colnames(df)
```

3. Calculate number of rows in a data set

```{r}
nrow(df)
```

4. Calculate number of columns in a data set

```{r}
ncol(df)
```

5. List structure of a data set

```{r}
str(df)
```

6. See first 6 rows (by default) of data set

```{r}
head(df)
```

7.	See first n rows of data set (Select to see the first 15 rows of data set)

```{r}
head(df, n = 15)
```

8. See all rows but the last row

```{r}
df[-nrow(df), ]
```

9. See last 6 rows (by default) of a data set

```{r}
tail(df)
```

10. See last n rows of data set (Select to see the last 12 rows of data set)

```{r}
tail(df, n = 12)
```

11.	See the last n rows but the first row

```{r}
df[-1, ]
```

12.	Number of missing values
```{r}
sum(is.na(df))
```

```{r}
colSums(is.na(df))
```

13. Number of missing values in a single variable

```{r}
sum(is.na(df$rating))
```

14.	Plot a simple graph, which will appear on a screen device.

```{r}
plot(x = df$rating, y = df$raises, main = 'Raises vs Rating', xlab = 'Rating', ylab = 'Raises')
```

15.	Plot the graph shown below, and make it appear on a file device (a pdf file)

```{r}
plot(x = df$privileges, y = df$learning, main = 'Learning Attitude', xlab = 'Privileges', ylab = 'Learning')
```

```{r}
pdf(file = 'learning-attitude.pdf', width = 4, height = 4)

plot(x = df$privileges, y = df$learning, main = 'Learning Attitude', xlab = 'Privileges', ylab = 'Learning')

dev.off()
```
